\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-11 paper/mswp2012-proposal.tex
added Pagebreak, just to make it pretty
introduction

The engineering part is split into different phases. This leads to the creation of a usable, rudimentary but integrated prototype after a short time. Nevertheless, the vision is a long-term development. For each phase it is necessary to find different partners in economy, politics, health-care and science. The partners mainly use our platform for advertisement and customer relationships, which brings benefits to them as well. \\

@@

\note{
\begin{itemize}
	\item {\em Length: 2-3 pages}
	\item {\bf Why?}
	\item Introduction
	\item Context
	\item What is the current situation?
	\item What is the open/unresolved problem or opportunity?
	\item Why is it a problem?
	\item What is unknown?
	\item What could be improved?
	\item Explanation of fundamental terms and basic definitions.
\end{itemize}
}

% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}

>>>>

The engineering part is split into different phases. This leads to the creation of a usable, rudimentary but integrated prototype after a short time. Nevertheless, the vision is a long-term development. For each phase it is necessary to find different partners in economy, politics, health-care and science. The partners mainly use our platform for advertisement and customer relationships, which brings benefits to them as well.

@@

%\note{
%\begin{itemize}
%	\item {\em Length: 2-3 pages}
%	\item {\bf Why?}
%	\item Introduction
%	\item Context
%	\item What is the current situation?
%	\item What is the open/unresolved problem or opportunity?
%	\item Why is it a problem?
%	\item What is unknown?
%	\item What could be improved?
%	\item Explanation of fundamental terms and basic definitions.
%\end{itemize}
%}

More and more people are getting obese. They live unhealthy and do to less sport. Many health-reports in Europe and America describe the problem and show how fast the people are getting fat. Particular bad are the children, which also gets unhealthy. And these children are going to become serious problems when they are grown up. \\

Studies\footnote{\url{http://www.sueddeutsche.de/gesundheit/gesundheitsbericht-des-rki-fast-ein-viertel-der-deutschen-ist-fettleibig-1.1382763}} show, that about 23 Percent of the people in Germany are obese nowadays. These people don’t only look bad. They can get serious health-problems like hypertension, diabetes and other cardiovascular problems.  \\

In near future this will cause a lot of financial claim in our health-care-system. More and more people have to get treated in a hospital because of health problems caused by being obese over the years.  \\

The only way we can reduce this costs in future, is to live nowadays healthier. And for this the software system should help. If people can get an bonus for living healthier, they will get motivated to do so. They will use the system in their live and reduce the risks to get one of the illnesses caused by obese.  \\

Every single person has a benefit when he uses the system. So he can live longer and healthier. We can say: \\
Mens sana in corpore sano \\
This Latin slogan means: In a healthier body is a healthier soul. People will feel happier, if they live healthier.  \\

Unfortunately it is not easy to motivate people to look on their own bodies. Many people are lazy and lay on the couch instead of going out for a walk. They buy junk food instead of fruits. Because they know how junk food tastes better. With this software system, the people should learn and accept a healthier way of living. They get a little benefit, when they buy an healthier fruit instead of junk food.  \\

These small benefits are combined in a challenge with all the other users of the system. So the motivation gets to a competition with a lot of other people living in a particular similar situation.  \\

Over all the health-care-system will lower the costs and so they can combine this system with their insurance-system. So people would have to use it for getting a cheaper insurance. So somebody who wants to live healthier can have a cheaper insurance.  \\

This project is accompanied by a scientific study. This study have to monitor the evolution of the health of the people while the use the system. This study show how efficient the system works. The iterative development of the system uses the data from the study for improving the output and to get healthier people.  \\

So everyone has a benefit with this system. The people are living healthier, happier and longer.  \\
% --------------------------------------------------------------
\section{Project goals and deliverables}
\label{sect:goals}
